---
title: "Homework9"
author: "Melanie Lashlee Adams"
date: "7/10/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(modelr)
library(knitr)
load("training.RData")
# For this assignment, use the lemons dataset, which is a subset of the dataset used for a Kaggle competition described here: https://www.kaggle.com/c/DontGetKicked/data.
```

## 1. Using the lemons dataset, plot the probability of a car being a bad buy by make.

Crosstab of `IsBadBuy` with the independent variable of `Make`

```{r}
tab_make<-with(training,table(Make,IsBadBuy))
```

Change the row and column titles

```{r}
colnames(tab_make)<-c("Not a Lemon","Lemon")
kable(tab_make)
```
Add proportions to this table.
```{r}
tab_make_prop<-prop.table(tab_make,margin=1)
kable(tab_make_prop)
```

Percentages
```{r}
kable(round(tab_make_prop*100,1))
```

Format data for barcharts.  Use the variable "Make" to calculate the probability of the car being a lemon. 

```{r}
training_sum <- training%>%
  group_by(Make)%>%
  summarise(prob_bb=mean(IsBadBuy,na.rm=T))
```

Plot with ggplot 

```{r}
gg1 <- ggplot(training_sum, aes(y=prob_bb, x=Make))+
  geom_bar(stat = "identity", position = "dodge")+
  labs(title = "Probability of Lemons", x="Make of Vehicle", y="Lemon")+
  theme(legend.title = element_blank())
gg1 <- gg1+geom_text(aes(label=round(prob_bb,2)),
                     position = position_dodge(width = .9),
                     vjust=.25)
gg1
```

## 2. Create a table that shows the probability of a car being a bad buy by make.

```{r}
prop.table(tab_make,margin=1)%>%kable()
```

## 3. Create a heatmap of the probability of a car being a bad buy by make and acquisition type.
## Note AcquisitionType is a category listed in the Carvana_Data_Dictionary.txt but doesn't exist in the data (training or test). I will use Color instead.

Quartiles
```{r}
training <- training%>%
  mutate(Make_quintile=ntile(Make,5),
         Color_quintile=ntile(Color,5))
```

Summary dataset showing probabilities of the outcome across all of the combined categories of the two independent variables. 

```{R}
training_sum<-training%>%
  group_by(Make_quintile,Color_quintile)%>%
  summarize(prob_make=mean(IsBadBuy,na.rm=TRUE))%>%
  arrange(-prob_make)
```

Remove missing data.

```{r}
trainin_sum<-training_sum%>%filter(!(is.na(Make_quintile)),!(is.na(Color_quintile)))
```

Plot it.

```{r}
gg<-ggplot(training_sum,
           aes(x=as.factor(Make_quintile),
               y=as.factor(Color_quintile),fill=prob_make))
gg<-gg+geom_tile()
gg<-gg+scale_fill_gradient(low="white",high="red")
gg<-gg+xlab("Make")+ylab("Color")
gg<-gg+theme(legend.title=element_blank())
gg
```


## 4. Create a plot of your choosing that shows the probability of a car being a bad buy by year and make.

```{r}
tab_make_year<-with(filter(training,
                           as.character(VehYear)!="Year of Car"),
                           table(Make,IsBadBuy))
```

*Outcome by "Make" AND "Year"*
```{r}
prop.table(tab_make_year,margin=1)%>%kable()
```

## Bar Graphs from Cross Tabs

Format data for barcharts, use of the concept of conditional means. 

```{r}
training2_sum<-training%>%
  group_by(VehYear,Make)%>%
  summarize(prob_lemon=mean(IsBadBuy,na.rm=TRUE))
```

Plot using ggplot commands:

```{r}
gg2<-ggplot(training2_sum,aes(y=prob_lemon,x=Make,fill=VehYear))
gg2<-gg2+geom_bar(stat="identity",position="dodge")
gg2<-gg2+xlab("Make")+ylab("Pr(Lemon)")
gg2<-gg2+theme(legend.title=element_blank())
gg2<-gg2+geom_text(aes(label=round(prob_lemon,2)),
                   position=position_dodge(width=.9),
                   vjust=-.25)
gg2
```
