---
title: "Homework 3"
author: "Melanie Lashlee Adams"
date: "05/29/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
```
## Loading the dataset for the assignment questions
```{r}
load("attrition.Rdata")
```

## 1. Create a graphic that shows the distribution of Monthly income

```{r}
##The code below creates a Histogram showing the distribution of monthly income 
gg<-ggplot(at,aes(x=MonthlyIncome))
gg<-gg+geom_histogram(binwidth = 20,fill="lightblue")


```

```{r}
gg<-gg+ylab("Count")+xlab("Monthly Income") ## x & y axis labels
gg<-gg+theme(axis.text.x = element_text(angle = 50, hjust = 1))
gg<-gg+ggtitle("Distribution of Monthly Income") ## Chart Title
gg
``` 
## 2. Create a graph that shows the average level of monthly income by field of education

```{r}

at_sum<-at%>%group_by(MonthlyIncome, EducationField)%>%
  summarize(mincome=mean(MonthlyIncome))%>%arrange(-mincome)
at_sum
```

```{r}
##Code to create a bar chart showing the average level of monthly income by field of education
gg<-ggplot(at_sum,aes(x=EducationField,y=mincome,
        fill=EducationField)) 
 gg<-gg+geom_bar(stat="identity",position="dodge")
gg<-gg+ylab("Mean of Monthly Income")+xlab("Education Field") ## x & y axis labels
gg<-gg+theme(axis.text.x = element_text(angle = 50, hjust = 1))
gg<-gg+ggtitle("Level of Monthly Income by Field of Education") 
gg
```

## 3. Create another graph that shows the average level of monthly income by field of education and gender
```{r}
at_sum<-at%>%group_by(MonthlyIncome, EducationField, Gender)%>%
  summarize(mincome=mean(MonthlyIncome))%>%arrange(-mincome)
at_sum
```

```{r}
gg<-ggplot(at_sum,aes(x=reorder(EducationField,mincome),
                      y=mincome,
                      fill=Gender))
 gg<-gg+geom_bar(stat="identity",position="dodge")
gg<-gg+facet_wrap(~Gender)
gg<-gg+coord_flip()
gg<-gg+ylab("Mean of Monthly Income")+xlab("Education Field")
gg<-gg+theme(axis.text.x = element_text(angle = 60, hjust = 1))
gg<-gg+ggtitle("Level of Monthly Income by Field of Education & Gender")
gg
```

## 4. Create a graph that shows average levels of monthly income by field of education, gender and job level (scale of 1-5, highest ranked employees are 5)
```{r}
at_sum<-at%>%group_by(MonthlyIncome, EducationField, Gender, JobLevel)%>%
  summarize(mincome=mean(MonthlyIncome))%>% 
  ungroup()%>%
  arrange(mincome)
at_sum
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
gg<-ggplot(at_sum,aes(x=fct_reorder(Gender,mincome),y=mincome))
gg<-gg+geom_bar(stat="identity",aes(fill=EducationField),position="dodge")
gg<-gg+facet_wrap(~Gender+JobLevel,ncol=4)
gg<-gg+ylab("Mean of Monthly Income")+xlab("Gender")##labels the x & y axis
gg<-gg+theme(axis.text.x = element_text(angle = 60, hjust = 1))
gg<-gg+ggtitle("Level of Monthly Income by Field of Education, Gender & Job Level")
gg
```
